%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://dylanrandle.github.io/}{\Large Dylan Labatt Randle}} & Email : \href{mailto:dylanrandle@g.harvard.edu}{dylanrandle@g.harvard.edu}\\
  \href{https://dylanrandle.github.io/}{dylanrandle.github.io} & Mobile : +1-647-641-1994 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harvard University, School of Engineering \& Applied Sciences}{Cambridge, MA}
      {Master of Science in Data Science;  GPA: 4.0}{Sep 2018 -- Present}
    \resumeSubheading
      {University of California at Berkeley, College of Engineering}{Berkeley, CA}
      {Bachelor of Science in Industrial Engineering \& Operations Research;  GPA: 3.9}{Sep 2012 -- May 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Institute of Applied Computational Science, Harvard University}{Cambridge, MA}
      {Research Assistant}{Nov 2018 -- Present}
      \resumeItemListStart
        \resumeItem{Generative Adversarial Networks}
          {Researching GANs for generative modeling of solutions to ordinary and partial differential equations.}
        \resumeItem{Computational Fluid Dynamics}
          {Researched neural network methods for turbulence modeling; demonstrated solutions to Reynolds-Averaged Navier Stokes equations.}
      \resumeItemListEnd

    \resumeSubheading
      {Hubdoc, Inc. (acquired by Xero Limited)}{Toronto, Canada}
      {Head Data Scientist}{Jan 2017 -- Jul 2018}
      \resumeItemListStart
        \resumeItem{Production Deep Learning System}
          {Developed and deployed production deep learning system using LSTMs \& CNNs for information extraction (i.e. entity recognition and classification) from financial documents. Greatly reduced labor costs (\$1-3MM/year) and increased speed of service (14,000x for 80\% of documents). Tech stack: Python, Keras, Postgres, Ansible, AWS.}
        \resumeItem{Business Analytics}
          {Conducted business analyses as needed: e.g. capacity planning of labor, anomaly detection of web scrapers, and prioritization of scraper maintenance. Built reports and data visualizations for intranet.}
        \resumeItem{Management}
          {Regularly presented results and recommendations to C-suite. Integral in crafting team strategy and roadmap. Coordinated with product and marketing teams. Involved in fundraising and presentations to investors. Delivered machine learning lecture to 60+ people.}
      \resumeItemListEnd

    \resumeSubheading
      {Bank of Montreal, Capital Markets}{Toronto, Canada}
      {Financial Products Analyst}{Summer 2014}
      \resumeItemListStart
        \resumeItem{Fixed Income Derivatives}
          {Conducted analyses of various debt products (swaps, swaptions, ABS, MBS). Wrote custom C\# algorithm to analyze relationship between delta-hedging frequency and returns for Canadian swaptions; found possible trading opportunities.}
        \resumeItem{Sales \& Trading}
          {Compiled daily summaries of trading activity. Reviewed and analyzed sales product pitches. Supported both sales and trading with various data analyses.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects (click titles for links)}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/dylanrandle/autograd}{Automatic Differentiation}}
      {Python package implementing automatic differentiation (forward and reverse mode). Additionally implemented gradient-based optimizers and provided extensive documentation.}
    \resumeSubItem{\href{https://dylanrandle.github.io/troll_classification}{Twitter Troll Classification}}
      {Achieved 96\% accuracy in classifying tweets as trolls, using a dataset of Twitter handles indicted for meddling in the 2016 U.S. presidential election.}
    \resumeSubItem{\href{https://dylanrandle.github.io/bayesgan.html}{Bayesian Generative Adversarial Networks}}
      {Paper review, implementation, and demo of Bayesian Generative Adversarial Networks.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python (numpy, pandas, scikit-learn, pytorch, keras, pymc3), SQL, C/C++, Javascript}
      \hfill
      \textbf{Technologies}{: AWS, Spark, OpenMP, MPI, Git}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
