%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Dylan Labatt Randle} % Your name
% \address{B-1 \\ II , U.P. 208016} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\url{dylanrandle@g.harvard.edu} \\ \url{dylanrandle.github.io}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%, School of Engineering \& Applied Sciences
{\bf Harvard University} \hfill { Cambridge, MA}
\\ {\em M.S. Data Science} \hfill {\em May 2020}
\\ Applied Computation Scholarship, Special Distinction in Teaching
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

%, College of Engineering
{\bf University of California, Berkeley} \hfill {Berkeley, CA}
\\ {\em B.S. Industrial Engineering \& Operations Research} \hfill {\em May 2016}
\\ High Honors, Dean's Honors, Phi Beta Kappa, Tau Beta Pi


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Expert & Python (Pytorch, Tensorflow, Scikit-learn, Statsmodels, Pandas, Numpy, Scipy) \\
Proficient & AWS (EC2, EMR, S3, Athena), Apache Hadoop \& Spark, Docker, SQL, Git \\
% Jupyter, Unix, Latex, Markdown
% Familiar & C/C++, Javascript \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Amazon Robotics}{North Reading, MA}{Data Scientist, Intern}{Jun 2019 - Aug 2019}

\item
    Developed machine learning package for proprietary internal project.

\item
    Built automated and scalable data pipeline for big data querying, cleaning, transformation, and loading (${\sim} 1 \times 10^{12}$ rows).
    Implemented clean, extensible API for feature selection, model training, hyperparameter tuning, and testing.
    Developed interpretable visualizations (e.g. PDP, SHAP) for model explanations.

\item
    Increased speed and reduced complexity of model development and analysis.
    Documented and published code to internal repositories.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Hubdoc}{Toronto, Canada}{Data Scientist}{Jan 2017 - Jul 2018}
\item
    Acquired by Xero for \$70 million USD.
    First data scientist hired.
    Hired and led team of two additional data scientists.
    Presented results and recommendations to leadership.
    Pitched machine learning products to investors.

%Delivered company-wide lectures, updates during all-hands, and built data visualizations for intranet.

\item
    Designed and developed valuable deep learning product for automated
    data extraction from millions of financial documents.
    Tested various models (LSTMs, GRUs, bi-LSTMs, CNNs) and
    problem formulations (word-level, character-level,
    pre-trained embeddings, positional encodings).
    Deployed fault-tolerant, asynchronous pipeline
    serving thousands of predictions per minute with few-second
    latency, including live monitoring and alerting.

\item
    Product celebrated by customers and praised by leadership for
    significant value added to sale of the company.
    Product and team now core to Xero AI products and strategy.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Harvard University}{Cambridge, MA}{Teaching Fellow}{Nov 2019 -- May 2020}

\item
    CS109a: Introduction to Data Science. Prepared lecture materials on boosting, neural networks, gradient descent, backpropagation, and regularization.
    Explanations and visualizations lauded by students for clarity and simplicity.

\item
    CS205: Computing Foundations for Computational Science.
    Led hands-on lab sections covering AWS, Docker, OpenACC, OpenMP, MPI, Hadoop, and Spark.
    Held weekly office hours and graded homework assignments and final projects.

\item
    Awarded Special Distinction in Teaching for exemplary teaching and leadership.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Taylor Statten Camps}{Algonquin Park, Canada}{Canoe Trip Guide}{Summers 2015, 2016}

\item
    Led 36 and 50-day canoe trips through remote Canadian wilderness. Responsible for groups of seven teenage boys. In charge of planning,
    safety, and navigation.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{BMO Capital Markets}{Toronto, Canada}{Financial Products Analyst}{May 2014 - Aug 2014}

\item
    Conducted analyses of interest rate swaps and swaptions.
    Developed algorithm to model relationship between delta-hedging frequency and expected returns for Canadian swaptions.
    Discovered potential market opportunities, results praised by traders.

\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
% RESEARCH & Projects
%----------------------------------------------------------------------------------------

\begin{rSection}{Research \& Applied Projects}

\begin{rSubsection}{GANs for Differential Equations}{}{}{}
  \item Developed novel method for unsupervised training of neural
  networks to solve differential equations. Leveraged generative
  adversarial networks (GANs) to learn the loss function.
  Demonstrated efficacy on a range of problems, increasing
  accuracy by orders of magnitude over previous methods.
\end{rSubsection}

\begin{rSubsection}{Interpretable Reinforcement Learning}{}{}{}

  \item Researched interpretable machine learning methods and
  their application to high-stakes reinforcement learning problems.
  Employed imitation learning to train rules-based models.

\end{rSubsection}

\begin{rSubsection}{Neural Architecture Search}{}{}{}

  \item Harvard Capstone project investigating Differentiable
  Architecture Search (DARTS) for scientific datasets. Results
  and blog post (Towards Data Science) viewed thousands of times.

\end{rSubsection}

%\begin{rSubsection}{Deep Generative Modeling}{}{}{}
%\item Project focused on various deep generative models (VAEs, GANs). Currently implemented a ResNet VAE which produces fairly realistic samples.
%\end{rSubsection}

Please see my website for all of my available work: \url{dylanrandle.github.io}

\end{rSection}

%----------------------------------------------------------------------------------------
% LEADERSHIP
%----------------------------------------------------------------------------------------

\begin{rSection}{Leadership Experience}

\begin{rSubsection}{Harvard Graduate Canadian Club}{Cambridge, MA}{Treasurer}{Sep 2019 - May 2020}

\item Co-organizer of activities aimed at engaging the community of Canadian graduate students.
\item Met with leaders of Canadian Embassy to plan future engagements.
\item Managed club finances, prepared budgets and fundraising requests.

\end{rSubsection}

\begin{rSubsection}{Alpha Pi Mu}{Berkeley, CA}{Vice President}{Sep 2015 - May 2016}

\item Berkeley Industrial Engineering \& Operations Research academic honors society.
\item Engaged faculty members to participate in program fostering student-faculty interaction and collaboration on research.

\end{rSubsection}

%\begin{rSubsection}{Orr's House}{Toronto, Canada}{Head of House}{Jan 2011 - Dec 2011}

%\item Elected by students as head of Orr's house at Upper Canada College. Responsible for holding weekly meetings, scheduling intramurals and social events, and meeting with new students. Placed first in annual house points competition.
%\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
% AWARDS & RECOGNITIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Recognitions}

\begin{rSubsection}{Harvard University}{Cambridge, MA}{School of Engineering \& Applied Sciences}{Aug 2018 - May 2020}

\item Applied Computation Scholarship: \$20,000 scholarship for research in data science.
\item Special Distinction in Teaching: For exemplary teaching and leadership during Spring semester 2020.

\end{rSubsection}

\begin{rSubsection}{University of California, Berkeley}{Berkeley, CA}{College of Engineering}{Sep 2012 - May 2016}

\item High Honors: Top 10\% of class at graduation.
\item Phi Beta Kappa: National academic honors society.
\item Tau Beta Pi: Engineering honor society.
\item Alpha Pi Mu: Industrial engineering honor society.
\item Dean's Honors: Top 10\% of class in each semester.
\item Kraft Award: Perfect GPA (4.0) after freshman year.

\end{rSubsection}

%\begin{rSubsection}{Upper Canada College}{Toronto, Canada}{High School}{Sep 2011 - Jun 2012}

%\item Higher Level Economics Prize: Top student in economics.
%\item Moderns Prize in French: Top student in french.
%\item General Proficiency Award: Top 10\% of class.

%\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% Workshops / Presentations
%----------------------------------------------------------------------------------------

\begin{rSection}{Delivered Talks}

\begin{rSubsection}{Harvard ComputeFest 2020}{Cambridge, MA}{Workshop Presenter}{Jan 2020}

  \item Developed and presented ``Notebook to Cloud" workshop to ${\sim} 100$ participants for Harvard IACS ComputeFest 2020. Led section on deploying Tensorflow sentiment analysis model with Docker.

\end{rSubsection}

\begin{rSubsection}{Toronto Machine Learning Summit}{Toronto, Canada}{Invited Speaker}{Nov 2017}

  \item Presented Hubdoc's deep learning infrastructure to group of ${\sim} 80$ data scientists and engineers. Discussed challenges and best practices for deploying deep learning with Tensorflow-Serving.

\end{rSubsection}

%\begin{rSubsection}{Hubdoc Machine Learning Lecture}{Toronto, Canada}{Speaker}{Nov 2017}

% \item Presented Hubdoc's deep learning infrastructure to group of ${\sim} 80$ data scientists and engineers. Discussed challenges and best practices for deploying deep learning with Tensorflow-Serving.

%\end{rSubsection}

\end{rSection}


\end{document}
